Should I Fuzz my Inputs or Improve my Test Suite? Lessons from Differential Testing Runtime Engines.

### 2018-07-03 paper/paper.tex
minor fix
updating paper (wip)

Figure~\ref{fig:workflow} illustrates the workflow of the
infrastructure we used in this study. Boxes denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cyclic icons denote repetition--the leftmost cyclic icon
indicates that each file in the input list will be analyzed in
separate and the rightmost icon indicates that a single file will be
processed multiple times in fuzzing mode. The bug-finding process
takes on input JS files from regression test suites of various JS
engines. Table~\ref{tab:test-suites} shows the JS sources we mined
from online repositories of various open-source engines. Overall, we
found a total of \Fix{XX} JS files.

\begin{table}[h]
  \centering
  \caption{\label{tab:test-suites}Test Suites\Fix{use path in the repo}}
  \begin{tabular}{ccc}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    \Fix{duktape} & - & - \\
    \Fix{jerryjs} & - & - \\
    \Fix{jsi} & - & - \\
    \Fix{tiny} & - & - \\
    \Fix{mozilla} & - & - \\
    v8.test.benchmarks.data & - & - \\
    webkit.jstests.es6 & - & - \\
    webkit.jstests.microbenchmarks & - & - \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team from April 12 to May
    24, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  \\
    \midrule    
    1  & 4/12 & \checkm & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978}      \\ 
    2  & 4/12 & \checkm & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979}      \\
    3  & 4/14 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}        \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749}        \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033}       \\
    6  & 4/25 & \checkm & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038}      \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065}
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} \\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}    \\
    \midrule    
    9  & 4/29 & \checkm & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}    \\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{\checkm} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} \\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156}
    \\
    \midrule    
    11 & 5/02 & \checkm & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197}\\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208}\\
    13 & 5/10 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} \\
    14 & 5/17 & \checkm & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} \\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} \\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} \\
    17 & 5/24 & \checkm & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943}\\
   \bottomrule     
  \end{tabular}
\end{table*}

@@

The goal of this study is to assess the impact of fuzzing in finding
bugs with differential testing.

\subsection{Constants.}~We used the following engines in
this study: Microsoft's Chakra~\Fix{cite}, Google's v8~\Fix{cite},
Mozilla's SpiderMonkey~\Fix{cite}, and Apple's JavaScriptCore
(WebKit)~\Fix{cite}. We selected these engines based on
popularity~\Fix{cite}. Considering fuzzing tools, we used
representatives of the most popular approaches to fuzzing. For
random-based fuzzing we used Radamsa~\cite{radamsa}; for
coverage-based fuzzing we used
\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
generative-based fuzzing we used
\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
be found elsewhere~\cite{fuzz-bart}.

@@

\section{Bugs Found}
\label{sec:results}

This section shows results obtained with our
infrastructure. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of 42
days. So far, ten of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any new bug on SpiderMonkey and V8; the bugs we
found were duplicates and were not reported. Finally, it is
worth noting that 7 of the 17 JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from seven different open
source engines, including a total of 30K test files.

\section{Results}

\subsection{Fuzzing versus No Fuzzing}

\subsection{Fuzzing Strategy}

>>>>

Figure~\ref{fig:workflow} illustrates the workflow of the
infrastructure we used in this study. Boxes denote encapsulation;
arrowed lines indicate control flow (dashed) and data flow
(filled). The cyclic icons denote repetition--the leftmost cyclic icon
indicates that each file in the input list will be analyzed in
separate and the rightmost icon indicates that a single file will be
processed multiple times in fuzzing mode. The bug-finding process
takes on input JS files from regression test suites of various JS
engines. Table~\ref{tab:test-suites} shows the JS sources we mined
from online repositories of various open-source engines. Overall, we
found a total of almost 36,5K JS files.

\begin{table}[h]
  \centering
  \caption{\label{tab:test-suites}Test Suites\Fix{use path in the repo}}
  \begin{tabular}{ccc}
    \toprule
    TestSuite & Source & \# JS files \\
    \midrule
    Duktape & \href{https://github.com/svaarala/duktape}{GitHub} & 997 \\
    JerryJS & \href{https://github.com/jerryscript-project/jerryscript}{GitHub} & 1.803 \\
    JSI & \href{https://github.com/technosaurus/jsish}{GitHub} & 99 \\
    Tiny-js & \href{https://github.com/gfwilliams/tiny-js}{GitHub} & 44 \\
    Mozilla & \href{-}{-} & 32414 \\
    V8.test.benchmarks.data & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 64 \\
    WebKit.jstests.es6 & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 605 \\
    WebKit.jstests.microbenchmarks & \href{https://github.com/svaarala/duktape/tree/master/tests/ecmascript}{GitHub} & 426 \\
   \bottomrule     
  \end{tabular}
\end{table}

@@

\begin{table*}[h!]
  \vspace{-3ex}
%  \scriptsize
  \centering
  \caption{List of bug reports issued by our team
    24, 2018.}
  \label{tab:bugs}
  \begin{tabular}{cccccccc}
    \toprule
    Issue\#    & Date & Fuzz & Engine  & Status  & \multicolumn{1}{c}{Url}  & Priority & Seed \\
    \midrule    
    1  & 4/12 & radamsa & Chakra   & \textbf{Fixed}  & \href{https://github.com/Microsoft/ChakraCore/issues/4978}{\#4978} & HI & webkit.jstests.es6 \\ 
    2  & 4/12 & radamsa & Chakra   & Rejected  & \href{https://github.com/Microsoft/ChakraCore/issues/4979}{\#4979} & HI & webkit.jstests.es6 \\
    3  & 4/14 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=184629}{\#184629}  & HI & webkit.jstests.es6    \\
    4  & 4/18 & \crossmark & JavascriptCore  & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=184749}{\#184749} & HI & JerryScriptjs.ecma      \\
    5  & 4/23 & \crossmark & Chakra  & \textbf{Confirmed}  & \href{https://github.com/Microsoft/ChakraCore/issues/5033}{\#5033} & HI & mozilla      \\
    6  & 4/25 & radamsa & Chakra  & \textbf{Fixed}     & \href{https://github.com/Microsoft/ChakraCore/issues/5038}{\#5038} & HI & JerryScriptjs.ecma   \\
    7  & 4/29 & \crossmark & Chakra  & \textbf{Confirmed}   &
    \href{https://github.com/Microsoft/ChakraCore/issues/5065}{\#5065} & HI & mozilla
    \\
    \midrule
    \multirow{2}{*}{8}  & \multirow{2}{*}{4/29} &  \multirow{2}{*}{\crossmark} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5067}{\#5067} & \multirow{2}{*}{HI} & \multirow{2}{*}{mozilla}\\
                        &  &                       &
    JavascriptCore & New &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185130}{\#185130}  &   & \\
    \midrule    
    9  & 4/29 & radamsa & JavascriptCore  & New  &    \href{https://bugs.webkit.org/show\_bug.cgi?id=185127}{\#185127}  & HI  & JerryScriptjs.ecma\\
    \midrule    
    \multirow{2}{*}{10} & \multirow{2}{*}{4/30}  & \multirow{2}{*}{radamsa} & Chakra & \textbf{Confirmed} &    \href{https://github.com/Microsoft/ChakraCore/issues/5076}{\#5076} & \multirow{2}{*}{HI} & \multirow{2}{*}{tinyjs.tests}\\    
                        &                        &        &
    JavascriptCore & New &
    \href{https://bugs.webkit.org/show\_bug.cgi?id=185156}{\#185156} &  & 
    \\
    \midrule    
    11 & 5/02 & radamsa & JavascriptCore  & New & \href{https://bugs.webkit.org/show\_bug.cgi?id=185197}{\#185197} & LO & mozilla \\
    12 & 5/02 & \crossmark & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185208}{\#185208} & HI & mozilla \\
    13 & 5/10 & radamsa & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5128}{\#5128} & HI & JerryScriptjs.regression \\
    14 & 5/17 & radamsa & Chakra & \textbf{Fixed} & \href{https://github.com/Microsoft/ChakraCore/issues/5182}{\#5182} & HI & v8.test.benchmarks\\
    15 & 5/17 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5187}{\#5187} & HI & webkit.jstests.es6\\
    16 & 5/21 & \crossmark & Chakra & \textbf{Confirmed} & \href{https://github.com/Microsoft/ChakraCore/issues/5203}{\#5203} & LO & mozilla\\
    17 & 5/24 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show\_bug.cgi?id=185943}{\#185943} & HI & webkit.jstests.es6\\
    18 & 6/26 & radamsa & JavascriptCore & New  & \href{https://bugs.webkit.org/show_bug.cgi?id=187042}{\#187042} & HI & JerryScriptjs.regression\\
    19 & 6/28 & \crossmark & Chakra & Confirmed  & \href{https://github.com/Microsoft/ChakraCore/issues/5388}{\#5388} & HI & webkit.jstests.es6\\
   \bottomrule     
  \end{tabular}
\end{table*}

@@

The goal of this study is to assess the impact of fuzzing in finding
bugs with differential testing. In this section, we discuss
the methodology applied to prepare our environment for the experiments.
The dependents and independents variables
will be discuss in Section~\ref{sec:results}.

\subsection{Engines.}~We used the following engines in
this study: Microsoft's Chakra~\cite{chakra2018repo}, Google's v8~\cite{v82018repo},
Mozilla's SpiderMonkey~\cite{spidermonkey2018repo}, and Apple's JavaScriptCore
(WebKit)~\cite{jsc2018repo}. We selected these engines based on
popularity~\Fix{cite}. Considering fuzzing tools, we used
representatives of the most popular approaches to fuzzing. For
random-based fuzzing we used Radamsa~\cite{radamsa}; for
coverage-based fuzzing we used
\Fix{AFL~\cite{afl}/libfuzzer~\cite{libfuzzer}?}, and for
generative-based fuzzing we used
\Fix{grammarinator,jsfunfuzz?}. Details on how these fuzzers work can
be found elsewhere~\cite{fuzz-bart}.

\subsection{Seeds.}~This section describes 
how we found valid javascript files based on 
existing sources on the open-source repositories.
Originally, we looking JS engines repositories that we 
support (ie. V8, SpiderMonkey, Chakra and JavascriptCore) getting
their regression suites and benchmarks testing involving javascript files.
In addition, we mined repositories from GitHub based on the following criteria:
\begin{itemize}
  \item The project must be an open-source project and at least 1K stars from community.
  \item The repository must have JavaScript tests included.
  \item The tests should be plug-and-play and/or easy integration.
\end{itemize}

We focused on JavaScript Engines for its capacity to testing the
interpreter with pure JS files. The Figure~\ref{fig:query} 
illustrates the query to the Github API as an HTTP request, the result 
is sorted in descending order of stars. Initially, we obtained
a total of \Fix{XX} projects. Manually, we follow the criteria to exclude 
invalid projects and we obtained a total of \Fix{XX} repositories.

\begin{figure}
  \centering
  \begin{lstlisting}
https://api.github.com/search/repositories?q=javascript-engine+stars:>=1000&sort=stars
  \end{lstlisting}
  \caption{\label{fig:query}
  Query to the GitHub API for JS engines projects that contains at least 1K of stars from community.\Fix{fix query}
  }
\end{figure}

Due the variance of engines implementations, many projects uses distinct frameworks for testing 
and require external libs to run their testing suites. We try to use only the JS file with minor fixes
to support our environment. These fixes are composed by an assertion function that throws an Error that
we can capture by our infraestruture. 
% For example to run the JerryScript tests it was necessary 
% use the unit-test package to run it, but with our changes we added the assertion
% does not have an assertion in the test file
% \Fix{add code to explain}

\subsection{Fuzzers}
Fuzzers grammar-based can generate a new file through a language grammar (ie. BNF).
Our infrastructure supports any grammar fuzzer with a few adjusts. However, 
we try to integrate several grammar-based fuzzers, for example 
Grammarinator~\footnote{https://github.com/renatahodovan/grammarinator}, QuickFuzz~\cite{grieco2016quickfuzz}
and \Fix{others fuzzers} to generate new JavaScript files based on grammar, but 
after several runs it was observed that this approach was ineffective
due the amount of invalid files and/or files without discrepancies. For example, if we ran 
Grammarinator to generate 1K JS files ten times with a random seed generation, we obtained
\Fix{XX\%} of valid files. Checking in our environment almost \Fix{XX\%}
are js files that shows undefined variables and due the differential testing in our environment
all engines will raise a SyntaxError and this approach was not relevant to our experiment.

\section{Bugs Found}
\label{sec:bugs}

This section shows results obtained with our
infrastructure. Table~\ref{tab:bugs} shows the list of bugs we
reported on issue trackers of different engines in the period of 42
days. So far, ten of the bugs we reported
were confirmed, two of which were fixed. One bug report we
submitted was rejected on the basis that the offending JS file
manifested an expected incompatibility across engine
implementations.
Note from the table that all bug
reports still waiting for confirmation are associated with the
JavaScriptCore engine (JSC). A closer look at the JSC issue tracker
showed that the triage process is very slow for that engine. As of
now, we did not find any new bug on SpiderMonkey and V8; the bugs we
found were duplicates and were not reported. Finally, it is
worth noting that 8 of the 19 JS files that manifested
discrepancies were \emph{not} produced with fuzzing (column
``Fuzz''). These are test files from suites of different engines. This
observation emphasizes the importance of continuously collecting test suites from
multiple sources; today, we use test suites from seven different open
source engines, including a total of 30K test files.

\section{Results}
\label{sec:results}

\Igor{
  In this section we discuss our findings to reach
  bugs in JS engines. Our experiments shows that fuzzing existents files
  still effective over the inputs without fuzzing.
}

@@

\subsection{Fuzzing versus No Fuzzing}
\Fix{nao entendi muito sobre essa subsection... 
seria explicacao do porque utilizar o fuzzing baseado nos nosso resultados?}
\Igor{
  Os engines JS mais populares foram arduamente testados ao longo dos últimos anos, 
  o sistema robusto nao significa que esta livre de bugs, ao contrario,
  estamos testando-o com simples entradas a partir de testes de regressao 
  de bugs previamente encontrados, porem estas entradas poderiam servir como seeds 
  para novos testcases. Partindo disso, realizar fuzzer em arquivos 
  existentes em projetos open-sources eh uma maneira de
  aumentar ainda mais a eficiencia destes engines, por exemplo o Google incentiva o 
  uso de fuzzers no seu ecossistema\cite{oss-fuzz,honggfuzz}.

  Nosso estudo revelou que dos \Fix{19} bugs reportados pelo nosso time, 
  apenas 8 nao foram fuzzados \Fix{42.1\%}, isso se da 
  a importancia tanto de utilizar fuzzing em arquivos de teste do proprio projeto,
  quanto em projetos distintos de mesma ordem, pois neste caso engines JS 
  devem interpretar arquivos, entao quanto mais entradas, melhores os resultados.
  \Fix{discuss}
}

\subsection{Fuzzing Strategy}
\Igor{
  Para realizar nossos experimentos, tivemos que decidir qual as 
  melhores abordagens para aumentar a efetividade dos fuzzers.
  Os fuzzers mutacionais se mostraram mais eficientes em relacao
  aos fuzzers geracionais, entao focamos neste ponto.
  Utilizamos os fuzzers radamsa, QuickFuzz e \Fix{others} nas suas configuracoes
  default para realizar a mutacao em arquivos existentes.
  O fuzzer radamsa eh um fuzzer mutacional agnostico de linguagem e possui algumas
  deficiencias para a nossa infraestrutura como a falta de uma gramatica para guiar a suas mutacoes, 
  pois muitas das vezes a unica mutacao ocorre em uma palavra dentro de um comentario por exemplo.
  O fuzzer QuickFuzz tem uma gramatica JS integrada e sua mutacao ocorre de forma mais robusta que o 
  radamsa, gerando arquivos mais relevantes.
  Nossa infraestrutura usa a library Esprima\footnote{cite esprima url} para garantir que o arquivo fuzzado
  é um arquivo de teste relevante, seguindo estes requisitos:
  \begin{itemize}
    \item it contains only unicode text
    \item it is parseable (i.e., it is structurally well-formed)
    \item it does not contain engine-specific functions  
    \item it does not empty
  \end{itemize}

}
